Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-04 chi/piecework/presentation/complexity.tex
checkin -- near finished

  \begin{columns}
  % \vspace{1mm}
  \only<1,4->{
  \begin{column}{0.33\textwidth}
  \centering
  Trains
  \begin{figure}
    \begin{overlayarea}{\textwidth}{4cm}
    \begin{minipage}[c][4cm]{\textwidth}
      \includegraphics[width=\textwidth]{figures/photo/train-engineer.jpg}
    \end{minipage}
    \end{overlayarea}
    % \caption{i wanna fly the train}
    \end{figure}
\end{column}

\only<1>{
    \begin{column}{0.66\textwidth}
      \begin{itemize}
        \item Train engineers were among the first skilled workers to experience piece--rate payment systems
        \item ``Efficiency experts'' occasionally came by to evaluate how long it took to do various jobs
        \item This led to slow--walking the job, to offset the fact that
              efficiency experts weren't accounting for liminal work.
      \end{itemize}
    \end{column}
  }
}

  \only<2,4->{
    \only<2>{
      \begin{column}{0.33\textwidth}
      \begin{itemize}
        \item Ford, Taylor, and others moved quickly
              monitor and measure professionals.
      \end{itemize}
      \end{column}
    }

  \begin{column}{0.33\textwidth}
    \centering
      Automobiles
      \begin{figure}
        \begin{overlayarea}{\textwidth}{4cm}
        \begin{minipage}[c][4cm]{\textwidth}
          \includegraphics[width=\textwidth]{figures/idk.png}
        \end{minipage}
        \end{overlayarea}
        % \caption{something something}
      \end{figure}
  \end{column}

@@

\begin{frame}{Ford}
    % Fordism

\begin{frame}{Comparisons}
% \framesubtitle{something else}
%   \begin{columns}
%   \begin{column}{0.5\textwidth}
%   % \section*{Piecework}
%      some text here some text here some text here some text here some text here

%   \end{column}

%   \begin{column}{0.5\textwidth}
%   % \section*{CrowdWork}
%      some text here some text here some text here some text here some text here

%   \end{column}
%   \end{columns}
\end{frame}

>>>>

  \begin{columns}
  % \vspace{1mm}
  \only<1,4->{
  \begin{column}{0.33\textwidth}
  \centering
  Trains
  \begin{figure}
    \begin{overlayarea}{\textwidth}{4cm}
    \begin{minipage}[c][4cm]{\textwidth}
      \includegraphics[width=\textwidth]{figures/photo/train_workers.jpg}
    \end{minipage}
    \end{overlayarea}
    % \caption{i wanna fly the train}
    \end{figure}
\end{column}

\only<1>{
    \begin{column}{0.66\textwidth}
      \begin{itemize}
        \item ``Efficiency experts'' measured how long it would take to do various jobs
        \item These measurements would be used to assign values for each specific task
        \item Train engineers performed work more slowly when inspectors were around
      \end{itemize}
    \end{column}
  }
}

  \only<2,4->{
    \only<2>{
      \begin{column}{0.33\textwidth}
      \begin{itemize}
        \item Fordism, Taylorism, and Scientific Management in full force
      \end{itemize}
      \end{column}
    }

  \begin{column}{0.33\textwidth}
    \centering
      Automobiles
      \begin{figure}
        \begin{overlayarea}{\textwidth}{4cm}
        \begin{minipage}[c][4cm]{\textwidth}
          \includegraphics[width=\textwidth]{figures/photo/ford_assembly_line.jpg}
        \end{minipage}
        \end{overlayarea}
        % \caption{something something}
      \end{figure}
  \end{column}

@@

\begin{frame}{Comparisons}
\begin{itemize}
  \item Limited range of tasks > arbitrary changes (building planes is easier than fixing trains)
  \item Has technology changed this? Yes
  \begin{itemize}
    \item Technology makes complex tasks relatively trivial
    \item Measuring workers is easier than ever
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Complexity}{Cab Drivers}
% \begin{columns}
  % \begin{column}{0.20\textwidth}
    % \begin{itemize}
    %   \item 
      % Cab drivers
    % \end{itemize}
  % \end{column}

  % \begin{column}{0.80\textwidth}
  \begin{figure}
  \includegraphics<1>[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \includegraphics<2>[width=\textwidth]{figures/photo/gps-map.jpg}

  \end{figure}
  % \end{column}
% \end{columns}
\end{frame}

\begin{frame}{Complexity}{Algorithmic Measurement}
    notes
    \begin{itemize}
      \item I'm thinking of pointing to UpWork's screen recording tool as a way to measure workers
      \item also maybe google analytics and other ways of tracking web--based workers
    \end{itemize}
\end{frame}

\begin{frame}{Implications}
  \begin{itemize}
    \item We make stronger assumptions about workers' abilities thanks to technology
    \item Evaluation remains difficult, but we're trying to find stopgap solutions through decomposition
    \item We're still not solving the problems of inherently subjectively judged work
  \end{itemize}
\end{frame}
